The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
@Giappo will love my pick for the MBD and BD symbol :-)

@@

\item Here we present our study with the aim of exploring 
when using a more complex MBD tree prior is warranted.

>>>>

\usepackage{bbm}
\usepackage{dsfont}

@@

\item Here we present our study with the aim of exploring 
when using a more complex MBD tree prior is warranted.
To do so, we simulate phylogenies using the MBD process, with
varying degrees of that process. To be explicit, we define
that degree, $s$, as the number of extinct and extant species created
during a co-occuring speciation event, 
$n_{\mathbb{M}}$, from the total number of extinct and extant species:

\begin{equation}
s = \frac{n_{\mathbb{M}}}{n_{\mathbb{M}} + n_{\mathbb{B}}}
\end{equation}

Here, $n_{\mathbb{B}}$ is the number of extinct and extant species created
during a default single-birth speciation event.
